---
title: "n2015_4"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse);library(haven);library(survey);library(tableone);library(mosaic)
```


This is the R markdown notebook for analysis of the paper on aortic dissection trends using the NIS database. 

year: 2015
period:q4
icd10

We need to replicate the same markdown document for the ICD-10 data here.


```{r read df into the notebook}

core <- read_csv("C:/Users/Salil/Desktop/NIS2015/nis2015core.csv") %>% tbl_df
hosp <- read_csv("C:/Users/Salil/Desktop/NIS2015/nis2015hospital.csv") %>% tbl_df
dx <- read_csv('C:/Users/Salil/Desktop/NIS2015/nis2015q4dx.csv') %>% tbl_df

names(core)

names(hosp)

names(dx) <- tolower(names(dx)) # convert all var to lowercase
dx %>% tbl_df
```


Will merge the df to keep only those with ICD 10 codes.
Start with hosp as they have the ones with ICD10 codes.

```{r}
df1 <- left_join(hosp, core, by = "hosp_nis")

df2 <- left_join(dx, df1, by = "key_nis")

n15.4 <- df2

names(n15.4) <- toupper(names(n15.4))

```



prior CABG V45.81 = Z95.1

```{r prior CABG}

pricabg <- as.character(c("Z951")) # prior MI 

a <- pricabg

n15.4$pricabg <- with(n15.4, ifelse((I10_DX1 %in% a | I10_DX2 %in% a | I10_DX3 %in% a | I10_DX4 %in% a  | I10_DX5 %in% a | I10_DX6 %in% a | I10_DX7 %in% a | I10_DX8 %in% a |I10_DX9 %in% a| I10_DX10 %in% a | I10_DX11 %in% a | I10_DX12 %in% a | I10_DX13 %in% a | I10_DX14 %in% a | I10_DX15 %in% a ), "yes","no"))

n15.4 %>% count(pricabg)

```
Remove patients with prior CABG.

```{r}
df3 <- n15.4 %>% filter(pricabg == "no")
```


saved df3 here... n2015_4.csv



```{r, echo = FALSE, tidy = TRUE, message = FALSE }
lita <- as.character(c("02100Z9"))

df3$lita <- with(df3,ifelse((I10_PR1 %in% lita | I10_PR2 %in% lita | I10_PR3 %in% lita | I10_PR4 %in% lita | I10_PR5 %in% lita),"yes","no"))

df3 %>% count(lita)

rita <- as.character(c("02100Z8"))

df3$rita <- with(df3,ifelse((I10_PR1 %in% rita | I10_PR2 %in% rita | I10_PR3 %in% rita | I10_PR4 %in% rita | I10_PR5 %in% rita),"yes","no"))

df3 %>% count(rita)

df3$bita <- with(df3, ifelse((lita == "yes" & rita == "yes"), "yes", "no"))

df3 %>% count(bita)

```


```{r, echo= TRUE, tidy = TRUE}
a <- as.character(c("021209W", "0210AW", "021249W","02124AW",
                  "021309W", "02130AW", "021349W","02134AW",
                  "021109F", "02110AF", "021149F","02114AF", "02100Z8", "02011Z9"))

df3$cabg <- with(df3, ifelse((I10_PR1 %in% a | I10_PR2 %in% a | I10_PR3 %in% a | I10_PR4 %in% a  | I10_PR5 %in% a | I10_PR6 %in% a | I10_PR7 %in% a | I10_PR8 %in% a |I10_PR9 %in% a| I10_PR10 %in% a | I10_PR11 %in% a | I10_PR12 %in% a | I10_PR13 %in% a | I10_PR14 %in% a | I10_PR15 %in% a ), "yes","no"))

df3 %>% count(cabg)

```



```{r keep only CABG}

df4 <- df3 %>% filter(cabg == "yes")

dim(df4)

```

```{r identify patients with valve surgery also}


# open valve repair/replacement - ICD 10 codes 

# aortic valve

avr <- as.character(c("02RF0JZ","02QF0ZZ","02RF07Z","02RF08Z","02F0KZ"))

# mitral valve repair - open approach

mvrepair <- as.character(c("027G0ZZ","02NG0ZZ","02QG0ZZ","02VG0ZZ"))

mvrep <- as.character(c("02RG0JZ","02RG07Z","02RG08Z","02RG0KZ"))

pvprep <- as.character(c("027H0DZ","027H0ZZ","02NH0ZZ","02RH0ZZ","02RH08Z","02RH0KZ","02RH0JZ"))

tvrep <- as.character(c("027J0ZZ","02NJ0ZZ","02QJ0ZZ"))


vs <- as.character(c("02RF0JZ","02QF0ZZ","02RF07Z","02RF08Z","02F0KZ",
                     "027G0ZZ","02NG0ZZ","02QG0ZZ","02VG0ZZ",
                     "02RG0JZ","02RG07Z","02RG08Z","02RG0KZ",
                     "027H0DZ","027H0ZZ","02NH0ZZ","02RH0ZZ","02RH08Z","02RH0KZ","02RH0JZ",
                     "027J0ZZ","02NJ0ZZ","02QJ0ZZ"))


a <- vs

df4$vs <- with(df4, ifelse((I10_PR1 %in% a | I10_PR2 %in% a | I10_PR3 %in% a | I10_PR4 %in% a  | I10_PR5 %in% a | I10_PR6 %in% a | I10_PR7 %in% a | I10_PR8 %in% a |I10_PR9 %in% a| I10_PR10 %in% a | I10_PR11 %in% a | I10_PR12 %in% a | I10_PR13 %in% a | I10_PR14 %in% a | I10_PR15 %in% a ), "yes","no"))

df4 %>% count(vs)

```
Remove patients who have had concomitant valve surgery done.


```{r remove valve patients}

df5 <- df4 %>% filter(vs == "no")

dim(df5)

```




```{r, ECHO = FALSE, tidy= TRUE}
hiv <- c("B20")

chrnlung <- c("J40",
"J410",
"J411",
"J418",
"J42",
"J430",
"J431",
"J432",
"J438",
"J439",
"J440",
"J441",
"J449",
"J4520",
"J4521",
"J4522",
"J4530",
"J4531",
"J4532",
"J4540",
"J4541",
"J4542",
"J4550",
"J4551",
"J4552",
"J45901",
"J45902",
"J45909",
"J45990",
"J45991",
"J45998",
"J470",
"J471",
"J479",
"J60",
"J61",
"J620",
"J628",
"J630",
"J631",
"J632",
"J633",
"J634",
"J635",
"J636",
"J64",
"J660",
"J661",
"J662",
"J668",
"J670",
"J671",
"J672",
"J673",
"J674",
"J675",
"J676",
"J677",
"J678",
"J679",
"J684")



dm <- c(
  "E0800",
  "E0801",
  "E0810",
  "E0811",
  "E089",
  "E0900",
  "E0901",
  "E0910",
  "E0911",
  "E099",
  "E1010",
  "E1011",
  "E109",
  "E1100",
  "E1101",
  "E1110",
  "E1111",
  "E119",
  "E1300",
  "E1301",
  "E1310",
  "E1311",
  "E139",
  "O24011",
  "O24012",
  "O24013",
  "O24019",
  "O2402",
  "O2403",
  "O24111",
  "O24112",
  "O24113",
  "O24119",
  "O2412",
  "O2413",
  "O24311",
  "O24312",
  "O24313",
  "O24319",
  "O2432",
  "O2433",
  "O24811",
  "O24812",
  "O24813",
  "O24819",
  "O2482",
  "O2483",
  "O24911",
  "O24912",
  "O24913",
  "O24919",
  "O2492",
  "O2493")

dmcx <- c(
  
  "E0821",
  "E0822",
  "E0829",
  "E08311",
  "E08319",
  "E08321",
  "E083211",
  "E083212",
  "E083213",
  "E083219",
  "E08329",
  "E083291",
  "E083292",
  "E083293",
  "E083299",
  "E08331",
  "E083311",
  "E083312",
  "E083313",
  "E083319",
  "E08339",
  "E083391",
  "E083392",
  "E083393",
  "E083399",
  "E08341",
  "E083411",
  "E083412",
  "E083413",
  "E083419",
  "E08349",
  "E083491",
  "E083492",
  "E083493",
  "E083499",
  "E08351",
  "E083511",
  "E083512",
  "E083513",
  "E083519",
  "E083521",
  "E083522",
  "E083523",
  "E083529",
  "E083531",
  "E083532",
  "E083533",
  "E083539",
  "E083541",
  "E083542",
  "E083543",
  "E083549",
  "E083551",
  "E083552",
  "E083553",
  "E083559",
  "E08359",
  "E083591",
  "E083592",
  "E083593",
  "E083599",
  "E0836",
  "E0837X1",
  "E0837X2",
  "E0837X3",
  "E0837X9",
  "E0839",
  "E0840",
  "E0841",
  "E0842",
  "E0843",
  "E0844",
  "E0849",
  "E0851",
  "E0852",
  "E0859",
  "E08610",
  "E08618",
  "E08620",
  "E08621",
  "E08622",
  "E08628",
  "E08630",
  "E08638",
  "E08641",
  "E08649",
  "E0865",
  "E0869",
  "E088",
  "E0921",
  "E0922",
  "E0929",
  "E09311",
  "E09319",
  "E09321",
  "E093211",
  "E093212",
  "E093213",
  "E093219",
  "E09329",
  "E093291",
  "E093292",
  "E093293",
  "E093299",
  "E09331",
  "E093311",
  "E093312",
  "E093313",
  "E093319",
  "E09339",
  "E093391",
  "E093392",
  "E093393",
  "E093399",
  "E09341",
  "E093411",
  "E093412",
  "E093413",
  "E093419",
  "E09349",
  "E093491",
  "E093492",
  "E093493",
  "E093499",
  "E09351",
  "E093511",
  "E093512",
  "E093513",
  "E093519",
  "E093521",
  "E093522",
  "E093523",
  "E093529",
  "E093531",
  "E093532",
  "E093533",
  "E093539",
  "E093541",
  "E093542",
  "E093543",
  "E093549",
  "E093551",
  "E093552",
  "E093553",
  "E093559",
  "E09359",
  "E093591",
  "E093592",
  "E093593",
  "E093599",
  "E0936",
  "E0937X1",
  "E0937X2",
  "E0937X3",
  "E0937X9",
  "E0939",
  "E0940",
  "E0941",
  "E0942",
  "E0943",
  "E0944",
  "E0949",
  "E0951",
  "E0952",
  "E0959",
  "E09610",
  "E09618",
  "E09620",
  "E09621",
  "E09622",
  "E09628",
  "E09630",
  "E09638",
  "E09641",
  "E09649",
  "E0965",
  "E0969",
  "E098",
  "E1021",
  "E1022",
  "E1029",
  "E10311",
  "E10319",
  "E10321",
  "E103211",
  "E103212",
  "E103213",
  "E103219",
  "E10329",
  "E103291",
  "E103292",
  "E103293",
  "E103299",
  "E10331",
  "E103311",
  "E103312",
  "E103313",
  "E103319",
  "E10339",
  "E103391",
  "E103392",
  "E103393",
  "E103399",
  "E10341",
  "E103411",
  "E103412",
  "E103413",
  "E103419",
  "E10349",
  "E103491",
  "E103492",
  "E103493",
  "E103499",
  "E10351",
  "E103511",
  "E103512",
  "E103513",
  "E103519",
  "E103521",
  "E103522",
  "E103523",
  "E103529",
  "E103531",
  "E103532",
  "E103533",
  "E103539",
  "E103541",
  "E103542",
  "E103543",
  "E103549",
  "E103551",
  "E103552",
  "E103553",
  "E103559",
  "E10359",
  "E103591",
  "E103592",
  "E103593",
  "E103599",
  "E1036",
  "E1037X1",
  "E1037X2",
  "E1037X3",
  "E1037X9",
  "E1039",
  "E1040",
  "E1041",
  "E1042",
  "E1043",
  "E1044",
  "E1049",
  "E1051",
  "E1052",
  "E1059",
  "E10610",
  "E10618",
  "E10620",
  "E10621",
  "E10622",
  "E10628",
  "E10630",
  "E10638",
  "E10641",
  "E10649",
  "E1065",
  "E1069",
  "E108",
  "E1121",
  "E1122",
  "E1129",
  "E11311",
  "E11319",
  "E11321",
  "E113211",
  "E113212",
  "E113213",
  "E113219",
  "E11329",
  "E113291",
  "E113292",
  "E113293",
  "E113299",
  "E11331",
  "E113311",
  "E113312",
  "E113313",
  "E113319",
  "E11339",
  "E113391",
  "E113392",
  "E113393",
  "E113399",
  "E11341",
  "E113411",
  "E113412",
  "E113413",
  "E113419",
  "E11349",
  "E113491",
  "E113492",
  "E113493",
  "E113499",
  "E11351",
  "E113511",
  "E113512",
  "E113513",
  "E113519",
  "E113521",
  "E113522",
  "E113523",
  "E113529",
  "E113531",
  "E113532",
  "E113533",
  "E113539",
  "E113541",
  "E113542",
  "E113543",
  "E113549",
  "E113551",
  "E113552",
  "E113553",
  "E113559",
  "E11359",
  "E113591",
  "E113592",
  "E113593",
  "E113599",
  "E1136",
  "E1137X1",
  "E1137X2",
  "E1137X3",
  "E1137X9",
  "E1139",
  "E1140",
  "E1141",
  "E1142",
  "E1143",
  "E1144",
  "E1149",
  "E1151",
  "E1152",
  "E1159",
  "E11610",
  "E11618",
  "E11620",
  "E11621",
  "E11622",
  "E11628",
  "E11630",
  "E11638",
  "E11641",
  "E11649",
  "E1165",
  "E1169",
  "E118",
  "E1321",
  "E1322",
  "E1329",
  "E13311",
  "E13319",
  "E13321",
  "E133211",
  "E133212",
  "E133213",
  "E133219",
  "E13329",
  "E133291",
  "E133292",
  "E133293",
  "E133299",
  "E13331",
  "E133311",
  "E133312",
  "E133313",
  "E133319",
  "E13339",
  "E133391",
  "E133392",
  "E133393",
  "E133399",
  "E13341",
  "E133411",
  "E133412",
  "E133413",
  "E133419",
  "E13349",
  "E133491",
  "E133492",
  "E133493",
  "E133499",
  "E13351",
  "E133511",
  "E133512",
  "E133513",
  "E133519",
  "E133521",
  "E133522",
  "E133523",
  "E133529",
  "E133531",
  "E133532",
  "E133533",
  "E133539",
  "E133541",
  "E133542",
  "E133543",
  "E133549",
  "E133551",
  "E133552",
  "E133553",
  "E133559",
  "E13359",
  "E133591",
  "E133592",
  "E133593",
  "E133599",
  "E1336",
  "E1337X1",
  "E1337X2",
  "E1337X3",
  "E1337X9",
  "E1339",
  "E1340",
  "E1341",
  "E1342",
  "E1343",
  "E1344",
  "E1349",
  "E1351",
  "E1352",
  "E1359",
  "E13610",
  "E13618",
  "E13620",
  "E13621",
  "E13622",
  "E13628",
  "E13630",
  "E13638",
  "E13641",
  "E13649",
  "E1365",
  "E1369",
  "E138",
  "P702")



hhrwchf <- c("I130")

hhrwhrf <- c("I132")

hhrwohrf <- c("I1310")

hhrwrf <- c("I1311")

hrenworf <- c("I129","I150","I151")

htn <- c(
  
  "I10",
  "O10011",
  "O10012",
  "O10013",
  "O10019",
  "O1002",
  "O1003",
  "O10911",
  "O10912",
  "O10913",
  "O10919",
  "O1092",
  "O1093")

htncx <- c("I160",
           "I161",
           "I169",
           "I674")

htnpreg <- c(    "O10111",
                 "O10112",
                 "O10113",
                 "O10119",
                 "O1012",
                 "O1013",
                 "O10211",
                 "O10212",
                 "O10213",
                 "O10219",
                 "O1022",
                 "O1023",
                 "O10311",
                 "O10312",
                 "O10313",
                 "O10319",
                 "O1032",
                 "O1033",
                 "O10411",
                 "O10412",
                 "O10413",
                 "O10419",
                 "O1042",
                 "O1043",
                 "O111",
                 "O112",
                 "O113",
                 "O114",
                 "O115",
                 "O119")

htnwchf <- c("I110")

htnwochf <- c("I119","I152","I158","I159")

hypo <- c(
  
  "E000",
  "E001",
  "E002",
  "E009",
  "E018",
  "E02",
  "E030",
  "E031",
  "E032",
  "E033",
  "E038",
  "E039",
  "E890")

liver <- c(
  
  "B180",
  "B181",
  "B182",
  "I8500",
  "I8501",
  "I8510",
  "I8511",
  "K700",
  "K702",
  "K7030",
  "K7031",
  "K7040",
  "K7041",
  "K709",
  "K7210",
  "K7211",
  "K7290",
  "K7291",
  "K730",
  "K731",
  "K732",
  "K738",
  "K739",
  "K740",
  "K741",
  "K742",
  "K743",
  "K744",
  "K745",
  "K7460",
  "K7469",
  "K754",
  "K7581",
  "K760",
  "K766",
  "K7689",
  "K769",
  "Z944")

lymph <- c("C8100",
           "C8101",
           "C8102",
           "C8103",
           "C8104",
           "C8105",
           "C8106",
           "C8107",
           "C8108",
           "C8109",
           "C8110",
           "C8111",
           "C8112",
           "C8113",
           "C8114",
           "C8115",
           "C8116",
           "C8117",
           "C8118",
           "C8119",
           "C8120",
           "C8121",
           "C8122",
           "C8123",
           "C8124",
           "C8125",
           "C8126",
           "C8127",
           "C8128",
           "C8129",
           "C8130",
           "C8131",
           "C8132",
           "C8133",
           "C8134",
           "C8135",
           "C8136",
           "C8137",
           "C8138",
           "C8139",
           "C8140",
           "C8141",
           "C8142",
           "C8143",
           "C8144",
           "C8145",
           "C8146",
           "C8147",
           "C8148",
           "C8149",
           "C8170",
           "C8171",
           "C8172",
           "C8173",
           "C8174",
           "C8175",
           "C8176",
           "C8177",
           "C8178",
           "C8179",
           "C8190",
           "C8191",
           "C8192",
           "C8193",
           "C8194",
           "C8195",
           "C8196",
           "C8197",
           "C8198",
           "C8199",
           "C8200",
           "C8201",
           "C8202",
           "C8203",
           "C8204",
           "C8205",
           "C8206",
           "C8207",
           "C8208",
           "C8209",
           "C8210",
           "C8211",
           "C8212",
           "C8213",
           "C8214",
           "C8215",
           "C8216",
           "C8217",
           "C8218",
           "C8219",
           "C8220",
           "C8221",
           "C8222",
           "C8223",
           "C8224",
           "C8225",
           "C8226",
           "C8227",
           "C8228",
           "C8229",
           "C8230",
           "C8231",
           "C8232",
           "C8233",
           "C8234",
           "C8235",
           "C8236",
           "C8237",
           "C8238",
           "C8239",
           "C8240",
           "C8241",
           "C8242",
           "C8243",
           "C8244",
           "C8245",
           "C8246",
           "C8247",
           "C8248",
           "C8249",
           "C8250",
           "C8251",
           "C8252",
           "C8253",
           "C8254",
           "C8255",
           "C8256",
           "C8257",
           "C8258",
           "C8259",
           "C8260",
           "C8261",
           "C8262",
           "C8263",
           "C8264",
           "C8265",
           "C8266",
           "C8267",
           "C8268",
           "C8269",
           "C8280",
           "C8281",
           "C8282",
           "C8283",
           "C8284",
           "C8285",
           "C8286",
           "C8287",
           "C8288",
           "C8289",
           "C8290",
           "C8291",
           "C8292",
           "C8293",
           "C8294",
           "C8295",
           "C8296",
           "C8297",
           "C8298",
           "C8299",
           "C8300",
           "C8301",
           "C8302",
           "C8303",
           "C8304",
           "C8305",
           "C8306",
           "C8307",
           "C8308",
           "C8309",
           "C8310",
           "C8311",
           "C8312",
           "C8313",
           "C8314",
           "C8315",
           "C8316",
           "C8317",
           "C8318",
           "C8319",
           "C8330",
           "C8331",
           "C8332",
           "C8333",
           "C8334",
           "C8335",
           "C8336",
           "C8337",
           "C8338",
           "C8339",
           "C8350",
           "C8351",
           "C8352",
           "C8353",
           "C8354",
           "C8355",
           "C8356",
           "C8357",
           "C8358",
           "C8359",
           "C8370",
           "C8371",
           "C8372",
           "C8373",
           "C8374",
           "C8375",
           "C8376",
           "C8377",
           "C8378",
           "C8379",
           "C8380",
           "C8381",
           "C8382",
           "C8383",
           "C8384",
           "C8385",
           "C8386",
           "C8387",
           "C8388",
           "C8389",
           "C8390",
           "C8391",
           "C8392",
           "C8393",
           "C8394",
           "C8395",
           "C8396",
           "C8397",
           "C8398",
           "C8399",
           "C8400",
           "C8401",
           "C8402",
           "C8403",
           "C8404",
           "C8405",
           "C8406",
           "C8407",
           "C8408",
           "C8409",
           "C8410",
           "C8411",
           "C8412",
           "C8413",
           "C8414",
           "C8415",
           "C8416",
           "C8417",
           "C8418",
           "C8419",
           "C8440",
           "C8441",
           "C8442",
           "C8443",
           "C8444",
           "C8445",
           "C8446",
           "C8447",
           "C8448",
           "C8449",
           "C8460",
           "C8461",
           "C8462",
           "C8463",
           "C8464",
           "C8465",
           "C8466",
           "C8467",
           "C8468",
           "C8469",
           "C8470",
           "C8471",
           "C8472",
           "C8473",
           "C8474",
           "C8475",
           "C8476",
           "C8477",
           "C8478",
           "C8479",
           "C8490",
           "C8491",
           "C8492",
           "C8493",
           "C8494",
           "C8495",
           "C8496",
           "C8497",
           "C8498",
           "C8499",
           "C84A0",
           "C84A1",
           "C84A2",
           "C84A3",
           "C84A4",
           "C84A5",
           "C84A6",
           "C84A7",
           "C84A8",
           "C84A9",
           "C84Z0",
           "C84Z1",
           "C84Z2",
           "C84Z3",
           "C84Z4",
           "C84Z5",
           "C84Z6",
           "C84Z7",
           "C84Z8",
           "C84Z9",
           "C8510",
           "C8511",
           "C8512",
           "C8513",
           "C8514",
           "C8515",
           "C8516",
           "C8517",
           "C8518",
           "C8519",
           "C8520",
           "C8521",
           "C8522",
           "C8523",
           "C8524",
           "C8525",
           "C8526",
           "C8527",
           "C8528",
           "C8529",
           "C8580",
           "C8581",
           "C8582",
           "C8583",
           "C8584",
           "C8585",
           "C8586",
           "C8587",
           "C8588",
           "C8589",
           "C8590",
           "C8591",
           "C8592",
           "C8593",
           "C8594",
           "C8595",
           "C8596",
           "C8597",
           "C8598",
           "C8599",
           "C860",
           "C861",
           "C862",
           "C863",
           "C864",
           "C865",
           "C866",
           "C880",
           "C882",
           "C883",
           "C884",
           "C888",
           "C889",
           "C9000",
           "C9001",
           "C9002",
           "C9010",
           "C9011",
           "C9012",
           "C9020",
           "C9021",
           "C9022",
           "C9030",
           "C9031",
           "C9032",
           "C960",
           "C962",
           "C9620",
           "C9621",
           "C9622",
           "C9629",
           "C964",
           "C969",
           "C96A",
           "C96Z",
           "D47Z9")

lytes <- c("E860",
           "E861",
           "E869",
           "E870",
           "E871",
           "E872",
           "E873",
           "E874",
           "E875",
           "E876",
           "E8770",
           "E8771",
           "E8779",
           "E878")

mets <- c("C770",
          "C771",
          "C772",
          "C773",
          "C774",
          "C775",
          "C778",
          "C779",
          "C7800",
          "C7801",
          "C7802",
          "C781",
          "C782",
          "C7830",
          "C7839",
          "C784",
          "C785",
          "C786",
          "C787",
          "C7880",
          "C7889",
          "C7900",
          "C7901",
          "C7902",
          "C7910",
          "C7911",
          "C7919",
          "C792",
          "C7931",
          "C7932",
          "C7940",
          "C7949",
          "C7951",
          "C7952",
          "C7960",
          "C7961",
          "C7962",
          "C7970",
          "C7971",
          "C7972",
          "C7981",
          "C7982",
          "C7989",
          "C799",
          "C7B00",
          "C7B01",
          "C7B02",
          "C7B03",
          "C7B04",
          "C7B09",
          "C7B1",
          "C7B8",
          "C800",
          "C801",
          "R180")




obese <- c("E6601",
           "E6609",
           "E661",
           "E662",
           "E668",
           "E669",
           "O99210",
           "O99211",
           "O99212",
           "O99213",
           "O99214",
           "O99215",
           "R939",
           "Z6830",
           "Z6831",
           "Z6832",
           "Z6833",
           "Z6834",
           "Z6835",
           "Z6836",
           "Z6837",
           "Z6838",
           "Z6839",
           "Z6841",
           "Z6842",
           "Z6843",
           "Z6844",
           "Z6845",
           "Z6854")


renlfail <- c(
  
  "N183",
  "N184",
  "N185",
  "N186",
  "N189",
  "N19",
  "Z4901",
  "Z4902",
  "Z4931",
  "Z4932",
  "Z9115",
  "Z940",
  "Z992")



chf <- c("I0981",
"I501",
"I5020",
"I5021",
"I5022",
"I5023",
"I5030",
"I5031",
"I5032",
"I5033",
"I5040",
"I5041",
"I5042",
"I5043",
"I50810",
"I50811",
"I50812",
"I50813",
"I50814",
"I5082",
"I5083",
"I5084",
"I5089",
"I509")



carddrg <- c(001:002, 215:236,
242:252, 253:254, 258:262,
265:267, 268:274, 280:293,
296:298, 302:303,
306:313) 

peridrg <- c(299:301)

renaldrg <- c(652, 656:661, 673:675,
              682:684, 686:700)

nervdrg <- c(020:042, 052:103)



ceredrg <- c(020:022, 034:039,064:072)


pulmdrg <- c(190:192, 202:203) 


  
diabdrg <- c(637:639) 


hypodrg <- c(625:627,643:645)


renfdrg <- c(652, 682:685)


liverdrg <- c(420:425, 432:434,441:446)


ulcedrg <- c(377:384)

hivdrg <- c(969:970,974:977)


leukdrg <- c(820:830,834:849)


cancdrg <- c(054, 055, 146:148, 180:182,374:376, 435:437, 
             542:544,582:585, 597:599, 656:658,686:688, 715:716, 
             722:724,736:741, 754:756, 826:830,843:849)

arthdrg <- c(545:547) 

nutdrg <- c(640:641)

anedrg <- c(808:812)



alcdrg <- c(894:897) 


coagdrg <- c(813)


htncxdrg <- c(077,078,304)


htndrg <- c(079,305)

psydrg <- c(885)

obesedrg <- c(619:621)


deprsdrg <- c(881)     
```

```{r}
df<- df5 

names(df) <- tolower(names(df))
names(df)
```




```{r}

# relabel dataframe as df

#df <- n2015

# cm_chf
df$cm_chf <- with(df, ifelse((i10_dx1 %in% chf| i10_dx2 %in% chf | i10_dx3 %in% chf | i10_dx4 %in% chf| 
                              i10_dx5 %in% chf| i10_dx6 %in% chf | i10_dx7 %in% chf|
                              i10_dx8 %in% chf | i10_dx11 %in% chf | i10_dx12 %in% chf | 
                              i10_dx13 %in% chf | i10_dx14 %in% chf | i10_dx15 %in% chf | 
                              i10_dx16 %in% chf| i10_dx17 %in% chf | i10_dx18 %in% chf | i10_dx19 %in% chf | i10_dx20 %in% chf ), 1, 0))


df %>% count(cm_chf)

# cm_aids

df$cm_aids <- with(df, ifelse((i10_dx1 %in% hiv| i10_dx2 %in% hiv | i10_dx3 %in% hiv | i10_dx4 %in% hiv| 
                                i10_dx5 %in% hiv| i10_dx6 %in% hiv | i10_dx7 %in% hiv|
                                i10_dx8 %in% hiv | i10_dx11 %in% hiv | i10_dx12 %in% hiv | 
                                i10_dx13 %in% hiv | i10_dx14 %in% hiv | i10_dx15 %in% hiv | 
                                i10_dx16 %in% hiv| i10_dx17 %in% hiv | i10_dx18 %in% hiv | i10_dx19 %in% hiv | i10_dx20 %in% hiv ), 1, 0))

df %>% count(cm_aids)

# cm_anemdef

anedrg <- as.character(anedrg)

df$cm_anemdef <- with(df, ifelse((drg %in% anedrg), 1, 0))

df %>% count(cm_anemdef)


```


prior mi 

```{r}
# prior mi

priormi <- as.character(c("I252"))

df$priormi <- with(df, ifelse((i10_dx1 %in% priormi| i10_dx2 %in% priormi | i10_dx3 %in% hiv | i10_dx4 %in% priormi| 
                                i10_dx5 %in% priormi| i10_dx6 %in% priormi | i10_dx7 %in% priormi|
                                i10_dx8 %in% priormi | i10_dx11 %in% priormi | i10_dx12 %in% priormi | 
                                i10_dx13 %in% priormi | i10_dx14 %in% priormi | i10_dx15 %in% priormi | 
                                i10_dx16 %in% priormi| i10_dx17 %in% priormi | i10_dx18 %in% priormi | i10_dx19 %in% priormi | i10_dx20 %in% priormi ), "yes", "no"))

df %>% count(priormi)

```

prior pci 

```{r}



priorpci <- as.character(c("Z9861"))

df$priorpci <- with(df, ifelse((i10_dx1 %in% priorpci| i10_dx2 %in% priorpci| i10_dx3 %in% priorpci| i10_dx4 %in% priorpci| 
                                i10_dx5 %in% priorpci| i10_dx6 %in% priorpci | i10_dx7 %in% priorpci|
                                i10_dx8 %in% priorpci | i10_dx11 %in% priorpci | i10_dx12 %in% priorpci | 
                                i10_dx13 %in% priorpci | i10_dx14 %in% priorpci | i10_dx15 %in% priorpci| 
                                i10_dx16 %in% priorpci| i10_dx17 %in% priorpci | i10_dx18 %in% priorpci | i10_dx19 %in% priorpci | i10_dx20 %in% priorpci ), "yes", "no"))

df %>% count(priorpci)
```


prior stemi


```{r}


stemi <- as.character(c("I201","I2101","I2102","I2109","I211","I2111","I2119","I212","I2121","I2129"))

df$stemi <- with(df, ifelse((i10_dx1 %in% stemi| i10_dx2 %in% stemi| i10_dx3 %in% stemi| i10_dx4 %in% stemi| 
                                i10_dx5 %in% stemi| i10_dx6 %in% stemi | i10_dx7 %in% stemi|
                                i10_dx8 %in% stemi | i10_dx11 %in% stemi | i10_dx12 %in% stemi | 
                                i10_dx13 %in% stemi | i10_dx14 %in% stemi | i10_dx15 %in% stemi| 
                                i10_dx16 %in% stemi| i10_dx17 %in% stemi | i10_dx18 %in% stemi | i10_dx19 %in% stemi | i10_dx20 %in% stemi ), "yes", "no"))

df %>% count(stemi)


```

carotid a disease 

```{r}

car <- as.character(c("I6529"))

df$carotid <- with(df, ifelse((i10_dx1 %in% car| i10_dx2 %in% car| i10_dx3 %in% car| i10_dx4 %in% car| 
                                i10_dx5 %in% car| i10_dx6 %in% car | i10_dx7 %in% car|
                                i10_dx8 %in% car | i10_dx11 %in% car | i10_dx12 %in% car | 
                                i10_dx13 %in% car | i10_dx14 %in% car | i10_dx15 %in% car| 
                                i10_dx16 %in% car| i10_dx17 %in% car | i10_dx18 %in% car| i10_dx19 %in% car | i10_dx20 %in% car ), "yes", "no"))

df %>% count(carotid)


```



```{r}

icd <- as.character(c("Z95810"))

df$icd <- with(df, ifelse((i10_dx1 %in% icd| i10_dx2 %in% icd| i10_dx3 %in% icd| i10_dx4 %in% icd| 
                                i10_dx5 %in% icd| i10_dx6 %in% icd | i10_dx7 %in% icd|
                                i10_dx8 %in% icd | i10_dx11 %in% icd | i10_dx12 %in% icd | 
                                i10_dx13 %in% icd | i10_dx14 %in% icd | i10_dx15 %in% icd| 
                                i10_dx16 %in% icd| i10_dx17 %in% icd | i10_dx18 %in% icd| i10_dx19 %in% icd | i10_dx20 %in% icd ), "yes", "no"))

df %>% count(icd)

```

```{r}

names(df)


write_csv(df, "H:/bita_nis/df/m2015_4.csv")

```

